R Notebook

### 2021-06-24 paper-calculations.Rmd
paper and figures

```{r}
selectivv[[3]] %>%
  count(category, apps, group, period, wt = number_of_users) %>%
  spread(group, n) %>%
  mutate(fua = `Functional area` - Cities, 
         woj = Voivodeship - `Functional area`) %>%
  select(category, apps, period, cities = Cities, fua, woj) %>%
  gather(geo, val, -apps, -period, -category) %>%
  mutate(geo = factor(geo, c("cities", "fua", "woj"),
                      c("Cities", "Functional UAs", "Provinces")),
         category  = factor(category, c("Transportation", "Delivery"))) %>%
  group_by(apps, geo) %>%
  mutate(index = val/val[1],
         diff = val-val[1],
         apps = factor(apps, c("Uber", "Bolt Driver", "iTaxi", "FREE NOW",
                               "Takeaway", "Wolt", "Glover",  "Bolt Courier"))) %>%
  ggplot(data = ., aes(x = as.factor(period), y = diff/1000, group = apps, color = apps)) +
  geom_line() +
  scale_color_brewer(type = "qual", palette = "Dark2") +  
  facet_grid(category ~ geo, scales = "free_y") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "The reference period (t0=2018.1)", 
       y = "Change in the number of users\n(in thousands)", color = "Apps") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.position = "bottom") ->  p1b

@@

```{r}
selectivv[[4]] %>%
  mutate(apps = factor(apps, c("Uber", "Bolt Driver", "iTaxi", "FREE NOW",
                             "Bolt Courier", "Takeaway", "Wolt", "Glover")),
         day = factor(day, c("Mondays-Thursdays", "Fridays-Sundays")),
         hour = str_replace(hour, "day", "daytime"),
         hour = str_replace(hour, "night", "nightime"),
         category  = factor(category, c("Transportation", "Delivery")))  %>%
  ggplot(data = ., aes(x = as.character(period), y = activity_time, color = apps, group = apps)) +
  geom_line() +
  geom_point() + 
  facet_nested(day ~ category +  hour + statistic)  +
  scale_color_brewer(type = "qual", palette = "Dark2", name = "Apps") +  
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1),
        legend.position = "bottom") +
  labs(x = "Half-year", y = "Time spent in the app") + 
  scale_y_continuous(breaks = seq(0,7,1))  -> p4

@@

selectivv[[3]] %>%
  filter((group == "Voivodeship" & region_name == woj) |
         (group == "Functional area" & region_name == lau) | 
         (group == "Cities" & region_name == city)) %>%
  mutate(region_name = str_replace(region_name, "Functional area - ", "FUA: "),
         group = factor(group, c("Cities", "Functional area", "Provinces"),
                        ordered = T),
         region_name = str_replace(region_name, "Warszawa", "Warsaw"),
         region_name = str_replace(region_name, "Kraków", "Crakow"))  %>%
  arrange(apps, period, group) %>%
  group_by(category, apps, period) %>%
  mutate(n = number_of_users - lag(number_of_users),
         n = ifelse(is.na(n), number_of_users, n),
         period = as.character(period),
         apps = factor(apps, c("Uber", "Bolt Driver", "iTaxi", "FREE NOW",
                               "Takeaway", "Wolt", "Glover",  "Bolt Courier"))) %>%
  ungroup() %>%
  mutate(region_name = factor(region_name, unique(region_name), ordered = T)) %>%
  ggplot(data = ., aes(x = period, y = n, group = apps, color = apps)) +
  geom_line() +
  facet_nested(category ~ region_name, scales = "free_y") + 
  scale_color_brewer(type = "qual", palette = "Dark2") +
  labs(x = "Period", y = "Change in the number of users", color = "Apps") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.position = "bottom") -> p1_annex

>>>>

```{r}
selectivv[[3]] %>%
  count(category, apps, group, period, wt = number_of_users) %>%
  spread(group, n) %>%
  mutate(fua = `Functional area` - Cities, 
         woj = Voivodeship - `Functional area`) %>%
  select(category, apps, period, cities = Cities, fua, woj) %>%
  gather(geo, val, -apps, -period, -category) %>%
  mutate(geo = factor(geo, c("cities", "fua", "woj"),
                      c("Cities", "Functional UAs", "Provinces")),
         category  = factor(category, c("Transportation", "Delivery"))) %>%
  group_by(apps, geo) %>%
  mutate(index = val/val[1],
         diff = val-val[1],
         apps = factor(apps, c("Uber", "Bolt Driver", "iTaxi", "FREE NOW",
                               "Takeaway", "Wolt", "Glover",  "Bolt Courier"))) %>%
  ggplot(data = ., aes(x = as.factor(period), y = diff/1000, group = apps, color = apps)) +
  geom_line() +
  geom_point() + 
  scale_color_brewer(type = "qual", palette = "Dark2") +  
  facet_grid(category ~ geo, scales = "free_y") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "The reference period (t0=2018.1)", 
       y = "Change in the number of users\n(in thousands)", color = "Apps") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.position = "bottom",
        legend.direction = "horizontal") +
  guides(color = guide_legend(nrow = 2, byrow = TRUE)) ->  p1b

@@

```{r}
selectivv[[4]] %>%
  mutate(apps = factor(apps, c("Uber", "Bolt Driver", "iTaxi", "FREE NOW",
                               "Takeaway", "Wolt", "Glover",  "Bolt Courier")),
         day = factor(day, c("Mondays-Thursdays", "Fridays-Sundays")),
         hour = str_replace(hour, "day", "daytime"),
         hour = str_replace(hour, "night", "nightime"),
         category  = factor(category, c("Transportation", "Delivery")))  %>%
  ggplot(data = ., aes(x = as.character(period), y = activity_time, color = apps, group = apps)) +
  geom_line() +
  geom_point() + 
  facet_nested(day ~ category +  hour + statistic)  +
  scale_color_brewer(type = "qual", palette = "Dark2", name = "Apps") +  
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1),
        legend.position = "bottom") +
  labs(x = "Half-year", y = "Time spent in the app") + 
  scale_y_continuous(breaks = seq(0,7,1)) +
  guides(color = guide_legend(nrow = 2, byrow = TRUE))  -> p4

@@

selectivv[[3]] %>%
  filter((group == "Voivodeship" & region_name == woj) |
         (group == "Functional area" & region_name == lau) | 
         (group == "Cities" & region_name == city)) %>%
  mutate(region_name = str_replace(region_name, "Functional area - ", "FUA: "),
         group = factor(group, c("Cities", "Functional area", "Provinces"),
                        ordered = T),
         region_name = str_replace(region_name, "Warszawa", "Warsaw"),
         region_name = str_replace(region_name, "Kraków", "Crakow"))  %>%
  arrange(apps, period, group) %>%
  group_by(category, apps, period) %>%
  mutate(n = number_of_users - lag(number_of_users),
         n = ifelse(is.na(n), number_of_users, n),
         period = as.character(period),
         apps = factor(apps, c("Uber", "Bolt Driver", "iTaxi", "FREE NOW",
                               "Takeaway", "Wolt", "Glover",  "Bolt Courier"))) %>%
  ungroup() %>%
  mutate(region_name = factor(region_name, unique(region_name), ordered = T)) %>%
  ggplot(data = ., aes(x = period, y = n, group = apps, color = apps)) +
  geom_line() +
  facet_nested(category ~ region_name, scales = "free_y") + 
  scale_color_brewer(type = "qual", palette = "Dark2") +
  labs(x = "Period", y = "Change in the number of users", color = "Apps") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.position = "bottom")  +
  guides(color = guide_legend(nrow = 2, byrow = TRUE))  -> p1_annex
